---
title: "indelsig.tools.lib"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette_indelsig}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Main Functions

- indel_classifier89(indels, genome.v): Segments the indels provided by adding the necessary information to generate the catalog
  - indels: data.frame of indels having as columns "Sample", "chr", "position", "REF", "ALT"
  - genome.v: either "hg19" or "hg38"
- indel_highspecific(indel.classified): Filters highly repeated indels (>= 10 repeats), indels with highly repeated nMer (>=10) and indels longer than 100 bps
  - indel.classified: the output of indel_classifier89
- gen_catalogue89(muts_list, sample_col):
  - muts_list: either the output of indel_classifier89 or indel_highspecific
  - sample_col: name or index of the column storing the sample names
- plots_indelprofile_89ch()

```{r}




```

